Fusing Filters with Integer Linear Programming

### 2014-05-13 2014betterfusionforfilters/section/02-CNF.tex
Caption of Figure 1

\begin{figure*}[ht!]
\begin{center}
\includegraphics[scale=0.5]{figures/ex1-compare.pdf}
\end{center}
\caption{Clusterings for normalize2 example: with stream fusion; our system; best imperative system}
\label{f:normalize2-clusterings}
\end{figure*}

% -----------------------------------------------------------------------------
\section{Combinator Normal Form}
\label{s:CombinatorNormalForm}
Each input program is expressed in \emph{Combinator Normal Form} (CNF), which is a textual description of its data flow graph. The grammar for CNF is in Figure~\ref{f:CombinatorNormalForm}. Both the @normalize@ and @normalize2@ examples on the previous page are in CNF, and the matching data flow graph for @normalize2@ is in Figure~\ref{f:normalize2-clusterings}. Our data flow graphs are similar to Loop Communication Graphs (LCGs) from related work in imperative array fusion~\cite{gao1993collective}. We name edges after the corresponding variable from the CNF form, and edges which are fusion preventing are drawn with a dash through them (as per the edge labeled @sum1@ in Figure~\ref{f:normalize2-clusterings}). In data flow graphs we tend to elide the worker functions to combinators when they are not important to the discussion --- so we don't show the @(+)@ operator on each use of @fold@.

>>>>

\begin{figure*}[ht!]
\begin{center}
\includegraphics[scale=0.5]{figures/ex1-compare.pdf}
\end{center}
\caption{Clusterings for normalize example: with stream fusion; our system; best imperative system}
\label{f:normalize2-clusterings}
\end{figure*}

% -----------------------------------------------------------------------------
\section{Combinator Normal Form}
\label{s:CombinatorNormalForm}
Input programs is expressed in \emph{Combinator Normal Form} (CNF), which is a textual description of its data flow graph. The grammar for CNF is in Figure~\ref{f:CombinatorNormalForm}. The @normalize@  examples on the previous page is in CNF, and the matching data flow graph for @normalize@ is in Figure~\ref{f:normalize2-clusterings}. Our data flow graphs are similar to Loop Communication Graphs (LCGs) from related work in imperative array fusion~\cite{gao1993collective}. We name edges after the corresponding variable from the CNF form, and edges which are fusion preventing are drawn with a dash through them (as per the edge labeled @sum1@ in Figure~\ref{f:normalize2-clusterings}). In data flow graphs we tend to elide the worker functions to combinators when they are not important to the discussion --- so we don't show the @(+)@ operator on each use of @fold@.
